D3064R0: OOTA Execution is Provably Vacuous

### 2023-12-05 ootavacuous.tex
Alan Stern December 4th feedback
Plus revert to old .pdf filename.

Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

\paragraph{Omitted Redundant Atomic Stores}
In contrast, a pair of back-to-back non-volatile atomic stores to \co{x}
might always be executed such that no other thread accesses \co{x}
during the time between those two stores.
This means that, short of inspecting the assembly code, the user has no
way of proving that the C++ implementation acted as if that store was
omitted from the source code.
In cases where this omission is undesirable, the user can resort to
volatile atomic stores or to inline assembly\footnote{
	For example, by placing the Linux-kernel \co{barrier()} macro
	between the two stores.
	This macro is an empty GCC \co{asm} that specifies the \co{memory}
	clobber.}
to prevent the compiler from omitting a store.
However, acting as if such a redundant store was omitted from the source
code cannot create an OOTA cycle because any valid execution (OOTA or not)
of the program with the first of a back-to-back pair of non-volatile
relaxed atomic stores omitted is essentially a valid execution of the
program with the store present.

>>>>

\paragraph{Omitted Redundant Atomic Stores}
In contrast, a pair of back-to-back non-volatile atomic stores to \co{x}
might always be executed such that no other thread accesses \co{x}
during the time between those two stores.
This means that, if the implementation acted as if the store was omitted
from the source, the user would have no way to prove that fact short of
inspecting the assembly code.
In cases where such omissions are undesirable, the user can resort to
volatile atomic stores or to inline assembly\footnote{
	For example, by placing the Linux-kernel \co{barrier()} macro
	between the two stores.
	This macro is an empty GCC \co{asm} that specifies the \co{memory}
	clobber.}
to prevent the compiler from omitting a store.
However, acting as if such a redundant store was omitted from the source
code cannot create an OOTA cycle because any valid execution (OOTA or not)
of the program with the first of a back-to-back pair of non-volatile
relaxed atomic stores omitted is essentially a valid execution of the
program with the store present.
